Case study validations of automatic bullet matching

### 2018-11-02 index.Rmd
Comment, add barrel info to the phoenix description

\hh{For the validation of the automatic matching algorithm we are considering three validation sets of -- what should be -- increasing difficulty level:} 
\begin{itemize}
\item {\bf Hamby set 44} 
Hamby set 44 is one set of the Hamby study \citep{hamby}. Each Hamby set  consists of a total of 35 bullets fired through ten consecutively manufactured barrels of Rugers P85. Each set consists of 20 known bullets (two from each of the ten barrels) and 15 questioned bullets of unknown origin. Note that all Hamby sets are closed sets; that is, all questioned bullets are fired through one of the ten barrels. The ammunition used for this set were 9 mm Luger 115 Grain Full Metal Jacket  from the Winchester Ammunition Company.
\item {\bf Phoenix PD}
Tylor Klep from Phoenix PD provided sets of known test fires and questioned bullets: the set of known bullets consists of three test fires (B1, B2, B3) from each of eight different barrels (A9, C8, F6, L5, M2, P7, R3, U10). Ten questioned bullets were provided (B, E, H, J, K N, Q, T, Y, Z). This set is an open set; that is,\ it is not known in advance whether all (or any) of the questioned bullets are fired from the known barrels.

Land engraved areas for each of the six lands of each bullet were scanned by Bill Henderson (Sensofar).
\item {\bf Houston FSI}
This study was set up by Melissa Nally and Kasi Kirksey from FSI Houston. Three test sets based on ten consecutively rifled Ruger LCP barrels (A, B, C, D, E, F, G, H, I, J) and three other, non-consecutively rifled Ruger LCP barrels (R1, R2, R3). Each test set consists of three test fires each from five consecutively rifled barrels. Additionally, ten questioned bullets are provided for each kit. The ammunition used in both test fires and the questioned bullets were Remington UMC 9mm Luger Full Metal Jackets. All three of the test sets are open; that is,\ not every one of the questioned bullets is fired from the five known barrels in each of the test set.
The structure of these three sets is similar to a forthcoming study by Nally and Kirksey, but the results here come from preliminary test sets made available to us.
\end{itemize}

@@

\svp{When evaluating classifier performance, it is common to use a receiver operating curve, which plots the false positives against the true positives for each possible value of the cutoff between the two classes (in this case, known match and known non-match). The ROC curves for the land-to-land scores are shown in \autoref{fig:rocs}. A perfect classifier would have 100\% true positives and 0\% false positives, e.g. the ROC curve would be a right angle at (0, 1). Classifiers with better performance will be closer to this corner of the plot. A random classifier would have an ROC curve that was a straight diagonal line through (0,0) and (1,1).}

>>>>

\hh{For the validation of the automatic matching algorithm we are considering three validation sets of -- what should be -- increasing difficulty level:} 
\begin{itemize}
\item {\bf Hamby set 44} 
Hamby set 44 is one set of the Hamby study \citep{hamby}. Each Hamby set  consists of a total of 35 bullets fired through ten consecutively manufactured barrels of Rugers P85. Each set consists of 20 known bullets (two from each of the ten barrels) and 15 questioned bullets of unknown origin. Note that all Hamby sets are closed sets; that is, all questioned bullets are fired through one of the ten barrels. The ammunition used for this set were 9 mm Luger 115 Grain Full Metal Jacket  from the Winchester Ammunition Company.
\item {\bf Phoenix PD}
Tylor Klep from Phoenix PD provided sets of known test fires and questioned bullets: the set of known bullets consists of three test fires (B1, B2, B3) from each of eight different Ruger P-95 barrels (A9, C8, F6, L5, M2, P7, R3, U10). Ten questioned bullets were provided (B, E, H, J, K N, Q, T, Y, Z). This set is an open set; that is,\ it is not known in advance whether all (or any) of the questioned bullets are fired from the known barrels.
\svp{Need to add ammo info here...}
Land engraved areas for each of the six lands of each bullet were scanned by Bill Henderson (Sensofar).
\item {\bf Houston FSI}
This study was set up by Melissa Nally and Kasi Kirksey from FSI Houston. Three test sets based on ten consecutively rifled Ruger LCP barrels (A, B, C, D, E, F, G, H, I, J) and three other, non-consecutively rifled Ruger LCP barrels (R1, R2, R3). Each test set consists of three test fires each from five consecutively rifled barrels. Additionally, ten questioned bullets are provided for each kit. The ammunition used in both test fires and the questioned bullets were Remington UMC 9mm Luger Full Metal Jackets. All three of the test sets are open; that is,\ not every one of the questioned bullets is fired from the five known barrels in each of the test set.
The structure of these three sets is similar to a forthcoming study by Nally and Kirksey, but the results here come from preliminary test sets made available to us.
\end{itemize}

@@

When evaluating classifier performance, it is common to use a receiver operating curve, which plots the false positives against the true positives for each possible value of the cutoff between the two classes (in this case, known match and known non-match). The ROC curves for the land-to-land scores are shown in \autoref{fig:roc-auc} (a). A perfect classifier would have 100\% true positives and 0\% false positives, e.g. the ROC curve would be a right angle at (0, 1). Classifiers with better performance will be closer to this corner of the plot. A random classifier would have an ROC curve that was a straight diagonal line through (0,0) and (1,1).
